---
title: "aligning and scaling and PCA"
output: html_document
---

`````{r}
rm(list=ls())
``````

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

````{r include=FALSE}
#library(lubridate)
library(dplyr)
library(data.table)
#library(stringr)
library(ggplot2)
library(Momocs)
#library(wesanderson)
#library(DescTools)
#library(PBSmapping)
#library(desc)
library(jtools)
library(Momocs)
library(tidyr)
library("ggimage")
````

## Preliminary data treatment

```{r}
a<-read.csv("resampled_scaled_smoothed_rotated_tulips_220820.csv")
# b<-read.csv("resampled_scaled_smoothed_rotated_carnations.csv")
a$motif_family<-"tulip"
# b$motif_family<-"carnation"

c<-a
length(unique(c$object_id))

c<-c%>%
  arrange(motif_family, object_id, point_order)
``````

sorting out some point order reversed images

``````{r}
fix<-c("BM27_0001_c","BM56_1_0004_t","NMS02_1_0000_t","SHM01_0008_t","VA59_3_0001_t")
redo<-c%>%
filter(object_id%in%fix)%>%
group_by(object_id)%>%
arrange(desc(point_order))%>%
mutate(point_order=1:240)%>%
arrange(point_order)%>%
  as.data.frame()
c2<-c%>%
filter(!object_id%in%fix)%>%
  as.data.frame()
c3<-rbind(c2, redo)
````````
subset to one family
```````{r}
c3<-c3%>%filter(motif_family=="tulip")
````````

## Scaling, centering, prelim aligning using Momocs

split the dataframe into matrixes of individual objects.
````{r}
a6<-split(c3,list(c3$object_id),drop=TRUE)
a7<-lapply(a6,function(x){as.matrix(x[,c(2,3)])})
a8<-Out(a7) #builds an outline coo object
````
scale
````{r}
a9<-a8%>%coo_scale
````````
centre on the origin
````{r}
a11<-a9%>%coo_centre
`````
unlist the scaled, centred, smoothed data
````{r}
a12<- unlist(lapply(a11, function(x) if(is.data.frame(x)) list(x) else x), recursive = FALSE)
a13<-do.call(rbind, a12)
names(a13)<-c("x", "y")
a13<-a13%>%
  arrange()
m<-c3%>%
  select(object_id, motif_family, point_order)%>%
  arrange(object_id, point_order)
a14<-cbind(a13, m)
``````

``````{r}
#ggplot(data=a14, aes(x=x, y=y))+
#geom_polygon(fill="grey", colour="grey", alpha=0.25, size=1)+
#geom_point(data=a14, aes(x=x, y=y, colour=point_order), size=1)+
#geom_point(data=a14, aes(x=x, y=y, colour=point_order), size=1)+
#ylim(-3,3)+
#xlim(-3,3)+
#guides(colour=FALSE)+
#facet_wrap(~object_id, ncol=34)+
#theme_void()+
#theme(aspect.ratio=1)+
#scale_colour_gradient(low="red", high="blue")+
#theme(strip.text.x = element_text(size = 10))
#ggsave(filename="all objects.pdf", plot = last_plot(),
#device = "pdf", scale = 1,width = 300,height = 300,units = c("cm"),dpi = 500, #limitsize = FALSE)
```````
make PCA data
``````{r}
a16<-pivot_wider(a14, -c(x), values_from=y, names_from=point_order)
pca_data_y<-a16%>%
select("1":"240")%>%
as.data.frame()
rownames(pca_data_y)<-as.character(a16$object_id)
pca_data_y<-pca_data_y

id <- sort(unique(a16$object_id), decreasing = FALSE)
a <- a14 %>% 
  group_by(object_id) %>% 
  arrange(desc(object_id)) %>%
  select(x, y)  %>%
  group_map(~ c(t(.x)))
aa <- data.frame(Reduce(rbind, a))
pcaraw <- cbind(id=id, aa)

coord <- pcaraw[,-1]
rownames(coord) <- pcaraw[,1]
```````
PCA
``````{r}
pca_data<-pca_data_y
pca<-princomp(pca_data)
scores<-pca$scores
scores<-as.data.frame(scores)
summary(pca)
scores<-scores%>%select(Comp.1:Comp.20)
scores$object_id<-rownames(scores)
m<-c3%>%
  select(object_id, motif_family)%>%
  unique()
scores<-merge(scores, m, by="object_id")
`````````
sample some objects for plotting as images and make them
```````{r}
left<-scores%>%filter(Comp.1<quantile(Comp.1, 0.01))%>%sample_frac(0.5)
right<-scores%>%filter(Comp.1>quantile(Comp.1, 0.99))%>%sample_frac(0.5)
bottom<-scores%>%filter(Comp.2<quantile(Comp.2, 0.01))%>%sample_frac(0.5)
top<-scores%>%filter(Comp.2>quantile(Comp.2, 0.99))%>%sample_frac(0.5)
middle<-scores%>%filter(Comp.1>quantile(Comp.1, 0.2) & Comp.1<quantile(Comp.1, 0.8) & Comp.2>quantile(Comp.2, 0.2) & Comp.2<quantile(Comp.2, 0.8))
middle<-middle%>%sample_n(15)
samp<-rbind(left, right, bottom, top, middle)

#samp<-scores%>%
#sample_n(50)
object_id<-sort(unique(as.character(samp$object_id)))
length(object_id)
for(i in object_id){
col<-scores%>%filter(object_id==i)
col<-col$colour
ggplot()+
geom_polygon(data=a14%>%filter(object_id==i), 
aes(x=x, y=y), fill="blue4", colour="grey50")+
theme_classic()+
guides(fill=FALSE)+
ylim(-2.5, 2.5)+
xlim(-2.5, 2.5)+
theme_void()+
theme(aspect.ratio=1)+
theme(strip.text.x = element_text(size = 10), 
panel.background = element_rect(fill = "white",colour = "white"))
name<-paste(i, ".jpg", sep ="")
print(name)
print(col)
ggsave(filename=name, plot = last_plot(),
device = "jpeg",
path = "imageforpcplot", scale = 1,width = 3,height = 3,units = c("cm"),dpi = 500)
}
```````

get address of images to plot
``````{r}
path="imageforpcplot"
file_name<- list.files(path=path, pattern = c("*.jpg"))
images<-as.data.frame(file_name)
images$object_id<-gsub("\\.jpg", "",images$file_name)
images$file_path<-file.path(path, images$file_name, fsep = .Platform$file.sep)
images<-merge(images, scores, by="object_id")
````````
plot PCs
```````{r}
#pal<-c("red", "blue")
ggplot()+
geom_point(data=scores, aes(x=Comp.1, y=Comp.2), alpha=0.5, size=0.5, colour="blue4")+
#scale_colour_manual(values=pal)+
geom_image(data=images, aes(x=Comp.1, y=Comp.2, image=file_path), size=0.1, image_fun= function(.) magick::image_transparent(., "white"))+
theme_classic()+
theme(aspect.ratio = 1)+
guides(colour=FALSE)+
scale_x_continuous(name="shape PC1")+
scale_y_continuous(name="shape PC2")
ggsave(filename="tulips_pcplot_1_2.pdf", plot = last_plot(),
device = "pdf", scale = 1,width = 10,height = 10,units = c("cm"),dpi = 500, useDingbats = FALSE)
``````


```````{r}
write.csv(scores, "all_tulips_shape_pca.csv", row.names=FALSE)
``````

look at outliers


out<-scores%>%
  filter(Comp.2>5)
out<-out$object_id


outdata<-comb%>%
  filter(object_id%in%out)
ggplot(outdata, aes(x=x, y=y, colour=point_order))+
geom_point(alpha=0.25)+
geom_polygon(alpha=0.25)+
facet_wrap(~object_id, ncol=3)+
ylim(-3,3)+
xlim(-3,3)+
theme_classic()+
theme(aspect.ratio = 1)

low<-scores%>%
  filter(Comp.2< -3)
low<-low$object_id
lowdata<-comb%>%
  filter(object_id%in%low)
ggplot(lowdata, aes(x=x, y=y, colour=point_order))+
geom_point(alpha=0.25)+
geom_polygon(alpha=0.25)+
facet_wrap(~object_id, ncol=3)+
ylim(-3,3)+
xlim(-3,3)+
theme_classic()+
theme(aspect.ratio = 1)

