---
title: "clustering colours of objects"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}

library(dplyr)
library(factoextra)
library(NbClust)
library(data.table)
```
get data
```{r}
files<- list.files(pattern = "*.csv")
````````
write results
``````{r}
path="/Users/Armand/Desktop/Iznik\ June\ 2020/clustering\ colours/clustering_results"
````````

`````{r}
files<-sample(files, 1)
````````
``````{r}
for(i in files){
a<-read.csv(i)
#a1<-scale(a)
a1<-as.matrix(a)
s<-fviz_nbclust(a1, kmeans, diss=NULL, method = c("silhouette"),k.max=40, iter.max=30)## silhouette estimation
w<-fviz_nbclust(a1, kmeans, diss=NULL, method = c("wss"),k.max=40, iter.max=30)## total sums squares estimation
sres<-s$data## combine all results in a data frame
sres<-as.data.frame(sres)
names(sres)<-c("clusters", "silhouette_width")
sres$sums_of_squares<-w$data$y
print(i)
write.csv(sres, file.path(path, paste("optimal_clustering", i, sep="_")), row.names=FALSE)
}
```````

